A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
remove more columns for tidier df

```{r classifyData}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(trial_ref = as.character(trial_ref)) %>%
   mutate(year = as.character(year)) %>%
   mutate(location = as.character(location)) %>%
   mutate(host_genotype = as.character(host_genotype)) %>%
   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
   mutate(replicates = as.integer(replicates)) %>%
   mutate(planting_date = ymd(planting_date)) %>%
   mutate(flowering_date = ymd(flowering_date)) %>%
   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
   mutate(fungicide_ai = as.character(fungicide_ai))%>%
   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2))%>%
   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
   mutate(total_fungicide = as.integer(total_fungicide)) %>%
   mutate(harvest_date = ymd(harvest_date)) %>%
   mutate(final_assessment = ymd(final_assessment)) %>%
   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4))%>%
   mutate(disease_error = round(as.double(disease_error), digits = 6))%>%
   mutate(D_error_type = as.character(D_error_type))%>%
   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4))%>%
   mutate(yield_error = round(as.double(yield_error), digits = 6))%>%
   mutate(Y_error_type = as.character(Y_error_type))%>%
   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6))%>%
   mutate(yield_gain = round(as.double(yield_gain), digits = 4))%>%
   mutate(prop_YG = round(as.double(prop_YG), digits = 4))%>%
   select(-c(trial_design, # remove the following columns
             plot_length.m.,
             plot_width.m.,
             plant_density,
             trade_name,
             n_treatment,
             emergence_date,
             rating_scale,
             raw_graded,
             raw_data_avail,
             comments,
             days_harvest.planting,
             AUDPS_m,
             AUDPC_sd,
             Inc_Ms,
             pod_fill_date,
             mid_late_pod_fill,
             yield_gain,
             Y_Msquare,
             prop_YG))
```

@@

```{r simpler_clusters_remove}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(spray_management != "Early_plus") %>%
   select(-c(fungicide_timing_1, # remove the following columns which no longer have use
             fungicide_timing_2,
             fungicide_timing_3))
```

@@

### Yield variance standardisation
```{r StandardiseYieldVariance}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      vi = 
         case_when(
            Y_error_type == "stdev" ~ disease_error ^2,
            Y_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      spray_management = fct_relevel(spray_management,sort)
   )

@@

### Disease severity variance standardisation
```{r StandardiseSeverityVariance}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      d_vi = 
         case_when(
            D_error_type == "stdev" ~ disease_error ^2,
            D_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management,sort)
   )

>>>>

```{r classifyData}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(trial_ref = as.character(trial_ref)) %>%
   mutate(year = as.character(year)) %>%
   mutate(location = as.character(location)) %>%
   mutate(host_genotype = as.character(host_genotype)) %>%
   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
   mutate(replicates = as.integer(replicates)) %>%
   mutate(planting_date = ymd(planting_date)) %>%
   mutate(flowering_date = ymd(flowering_date)) %>%
   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
   mutate(fungicide_ai = as.character(fungicide_ai))%>%
   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2))%>%
   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
   mutate(total_fungicide = as.integer(total_fungicide)) %>%
   mutate(harvest_date = ymd(harvest_date)) %>%
   mutate(final_assessment = ymd(final_assessment)) %>%
   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4))%>%
   mutate(disease_error = round(as.double(disease_error), digits = 6))%>%
   mutate(D_error_type = as.character(D_error_type))%>%
   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4))%>%
   mutate(yield_error = round(as.double(yield_error), digits = 6))%>%
   mutate(Y_error_type = as.character(Y_error_type))%>%
   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6))%>%
   mutate(yield_gain = round(as.double(yield_gain), digits = 4))%>%
   mutate(prop_YG = round(as.double(prop_YG), digits = 4))%>%
   select(-c(trial_design, # remove the following columns
             plot_length.m.,
             plot_width.m.,
             plant_density,
             trade_name,
             n_treatment,
             emergence_date,
             rating_scale,
             raw_graded,
             raw_data_avail,
             comments,
             days_harvest.planting,
             AUDPS_m,
             AUDPC_sd,
             Inc_Ms,
             pod_fill_date,
             mid_late_pod_fill,
             yield_gain,
             Y_Msquare,
             prop_YG,
             AUDPC_m,
             AUDPC_sd))
```

@@

```{r simpler_clusters_remove}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(spray_management != "Early_plus") %>%
   select(-c(fungicide_timing_1, # remove the following columns which no longer have use
             fungicide_timing_2,
             fungicide_timing_3,
             fungicide_application_1,
             fungicide_application_2,
             fungicide_application_3,
             fungicide_application_4,
             fungicide_application_5,
             fungicide_application_6,
             fungicide_application_7,
             ))
```

@@

### Yield variance standardisation
```{r StandardiseYieldVariance}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      vi = 
         case_when(
            Y_error_type == "stdev" ~ disease_error ^2,
            Y_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      spray_management = fct_relevel(spray_management,sort)
   ) %>%
   select(-c(yield_error,
             Y_error_type))

@@

### Disease severity variance standardisation
```{r StandardiseSeverityVariance}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      d_vi = 
         case_when(
            D_error_type == "stdev" ~ disease_error ^2,
            D_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management,sort)
   ) %>%
   select(-c(disease_error,
             D_error_type))
